Initial Analysis

### 2020-03-04 Initial_Analysis.Rmd
Final details on analysis

@@

1. Determine which countries have Neighbouring EEZs  
1.1. For this we used the Sea Around Us EEZ map that discriminate by oceans and a routine (*Estimate Transboundary Species*) to identify Neighbouring polygons,
1.2. Then we match the SAU spatial information (e.g. INDEX within EEZ and coordinates) with the Neighbouring data

2. Overlap distribution maps with Neighbours data  
2.1. For each species we merged the Neighbours data with their known distribution (SAU distribution and catch,ESMs, and Observation)  
3. Determine transboundary if:  
3.1. Species is present in both Neighbouring EEZs by INDEX

We create two "confidence level" based on data and area covered, i.e;

-
-

@@

This part is to determine the list of species to be analized in the project. Initially this list was limited by the species data from the DBEM, however, as we are not using the DBEM, the limit is now the SAU.

@@

## Determine Neighbourds

This is the first step of the analysis and will determine what EEZs are neighbouring. THe routine creates a final dataset that we then use to estimate transboundary species.

@@

This function determines what EEZs are Neighbours and returns a data.frame of it

@@

### Sub Routine; Neighbours

@@

Once those tresholds are met, the status of the species is determined as follows:

@@

The datasets SAU_D, OCC, and ESM are used as sppecies presence while SAU_C is used as a confirmation of that. The `Model Index` is the first treshold and estimates the uncertanty of models. Goes from 0 - 1 as follows:

- 1 or 0; All models agree that in the presence of the species
- 0.75; Three out of four models agree on speices presence
- 0.50; Two out of four models agree on speices presence
- 0.25; Only one model flags a speices presence
- 0; All models agree there is no species there

The `Area_Index` is the second treshold and estimates the proportion of each species distribution in each EEZ. It only take into consideration the distribution of the species within the two EEZs, rather than the complete distribution. Hence, is mirrord (e.g. if EEZ#1 is 0.40, EEZ#2 is 0.6)

@@

There are quite a few inconsistencies between the names of territories within the SAU shapefile, the distribution data and the UN database. The following function cleans up the names, some of them manually some of the automatic. It also removes the "transboundary nature" of those species shared by two territories that belong to the same nation (e.g. Brazil mainland and Brazil (Fernando de Noronha) or US Gulf of Mexico and US East coast). Finally, there is an annoying thing coding issue between MAC and Windows related to characters so I have to also fix for that, manually.

@@

  if(Variable_Selected == "catch"){
    Map_Label <- "Catch (Thousand Tonnes)"
    Plot_Name <- "Catch_plot.png"
  }else{
    Map_Label <- "Revenue (Million USD)"
    Plot_Name <- "Rev_plot.png"
  }

@@

  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-1500, max_Rev_lim) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal() +
    theme(
      legend.position = c(0.73,0.60),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
    # Base line
    # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
    #              colour = "black", size=0.1, inherit.aes = FALSE) +
    coord_polar(start = 0) + 
    geom_text(data=label_data_rev, 
              aes(x=id,
                  y=Value_sum+10,
                  label=sub_region,
                  hjust=hjust), 
              color="black",
              fontface="bold",
              size=2, 
              angle= label_data_rev$angleb, 
              inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,12000),
                         breaks = seq(0,12000,3000)) +
    guides(fill = guide_colorbar(label.position = "left")
    )

@@

  Catch_Plot <- ggplot(data = Subregion_Catch_Data,
                     aes(x=reorder(id,Value_sum),
                         y=Value_sum, 
                         fill=Value_sum
                     )
) +    
  ylim(-1.5, max_Catch_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Catch_Data,
             aes(
               x=reorder(id,Value_sum),
               y=Value_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sd's
  geom_errorbar(data = Subregion_Catch_Data,
    aes(
      ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd),
      ymax=Value_m+Value_sd
    ), 
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_catch, 
            aes(x=id,
                y=ifelse(Value_sum == 12,Value_sum,Value_sum+0.1), # Fix names overlap
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_catch$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       limits = c(0,12),
                       breaks = seq(0,12,3),
                       colours = pal
  )

@@

  plot_all <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
  # Labeks
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0, 0), 
                  y = c(1, 0.45)
  ) +
  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
                  size = 8,
                  x = c(0.330,0.485), 
                  y = c(0.31,0.29)
  )

@@

In here we load and cleaned the multiple external datasets requred to produce the manuscript figures

@@

## Determine Tresholds

Determine transboundary stocks and countries based on selected trsholds. We created two tresholds (levels of uncertanty), in here we can chose which level we wanna work with.

@@

@@

###_________________###
# Discrete species
###_________________###

@@

# Both categories (trans and Discrete)
Tresholded_T_Data %>% 
  semi_join(Discrete,
            by = "taxon_key") %>% 
  group_by(taxon_key) %>% 
  summarise(n()) %>% 
  pull(unique(taxon_key)) %>% 
  length()

n_discrete <- length(unique(Discrete$taxon_key))

  Summary_Discrete_B <- Discrete_B %>% 
  left_join(SAU_Sampled_Data,
           by = c("taxon_key","eez_name")) %>% 
  group_by(Variable) %>%
  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
         Per_SAU = Total_Discrete/Total_Global*100)

###_________________###
# Discrete Exclusive
###_________________###

@@

@@

Summary_Discrete_Exclusive <- Discrete %>% 
  left_join(SAU_Sampled_Data) %>% 
  group_by(Variable) %>%
  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
         Per_SAU = Total_Discrete/Total_Global*100)

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area, 
            by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    # Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T) #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>% # Momentaneus fix for some reason there are diff. between datasers
  # Match the sacle limits of both value and and catch 
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area, by = "fishing_entity") %>% 
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_Entity/1000000))
  ) %>% 
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
  group_by(fishing_entity,Variable,Value) %>% 
  summarise(
    Bins = cut(Value,breaks = Map_Breaks, dig.lab = 5 ),
    Bins_Plot = cut(Value,breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  # Convert catch to million tonnes
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value)
  )

@@

Subregion_Trans_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(Value_sum = sum,
                            Value_m = mean,
                            Value_sd = sd),
               na.rm=T) %>%
  # select(-Size_Entity,-Trans_Entity_n) %>% 
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),4)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

# Fix names for plot
Subregion_Trans_Value$sub_region <- Subregion_Trans_Value$sub_region %>% 
  gsub("Northern","N.",.) %>% 
  gsub("Southern","S.",.) %>% 
  gsub("Western","W.",.) %>% 
  gsub("Eastern","E.",.)

@@

# Label info Rev
label_data_rev <- Subregion_Trans_Value %>% 
  filter(Variable == "value") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
  )

# Label info Catch
label_data_catch <- Subregion_Trans_Value %>% 
  filter(Variable == "catch") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
  )

@@

# Variable to plot (value or catch)
Variable_plot <- "catch"
CreateFigureOne(Variable_plot)

@@

  p<- ggdraw() +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0, y = 0, width = 0.8, height = 1) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.4, y = 0, width =0.8, height = 1) +
  # Legend
  draw_plot(legend_plot, x = 0.2, y = 0.1, width = 0.59, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("A", "B"),
                  size = 15,
                  x = c(0.1, 0.6),
                  y = c(1, 1)
  ) +
  draw_plot_label(
    label = c("Revenue (USD) | Catch (Tones)","Million per Km2"),
                  size = 6,
                  x = c(0.3,0.40),
                  y = c(0.25,0.22)
  )

@@

Top_Rev_Countries <- c("Peru", "Russian Federation", "Chile", "USA")

Total_Top_Rev <- Value_Trans_Country %>% 
  filter(Variable == "value") %>% 
  filter(fishing_entity %in% Top_Rev_Countries) %>% 
  select(1:3)

@@

Top5 <- c("Peru", "Russian Federation", "Chile", "USA","China")

@@

### Statistical differences

We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.

@@

# ### Prepare Data
# Subregion_Data_stats <- Revenue_Country %>% 
#   left_join(Catch_Country,
#             by = "fishing_entity") %>% 
#   left_join(UN_Regions,
#             by = "fishing_entity") %>% 
#   mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
#   select(fishing_entity,sub_region,Total_USD,fishing_entity_catch)

@@

Catch_aov <- aov(fishing_entity_catch~sub_region, data = Subregion_Catch_stats)
Catch_aov

summary(Catch_aov)

# sub_region   16  50.63   3.164   3.767 7.2e-06 ***
# Residuals   155 130.22   0.840                    
# ---
# Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

#  Post-hoc analysis
TukeyHSD(Catch_aov)

@@

#  Post-hoc analysis
TukeyHSD(Rev_aov)
```

@@

# Number of coastal nations
length(unique(Status_Data_Plot$individual))

@@

Status_Data_Plot %>% 
  mutate(value = ifelse(value <0, value*-1,value)) %>% 
  group_by(observation) %>% 
  summarise(tot=sum(value),
            mean(value),
            sd(value)) %>% 
  arrange(desc(tot)) %>% 
  view()

@@

@@

# -------------------------- #
# Transboundary species
# -------------------------- #

Status_Data_Stats <- Status_Data_Plot %>% 
  filter(observation != "No Category") %>%
  mutate(value = abs(value)) %>%

Total_Trans_Status <- Status_Data_Stats %>% 
  group_by() %>% 
  summarise(sum = sum(value)) %>% 
  pull()

Status_Data_Stats %>% 
  group_by(observation) %>% 
  summarise_if(is.numeric,
               .funs = c(Mean="mean",
                           sd = "sd",
                          Sum = "sum")
  ) %>% 
  mutate(Sum/Total_Trans_Status*100)

# --------------------- #
### Check for Asumptions
# --------------------- #

>>>>

# Read Me
This script runs the analysis for the manuscript *Marine species do not need visas: the transboundary nature of the world’s exploited marine species* from the data loading to the results analysis. Is divided in two parts; *Methods* where the raw data is analyzed and *Results* where the results from the analysis are processed.

@@

1. Determine which countries have Neighboring EEZs  
1.1. For this we used the Sea Around Us EEZ map that discriminate by oceans and a routine (*Estimate Transboundary Species*) to identify Neighbouring polygons,
1.2. Then we match the SAU spatial information (e.g. INDEX within EEZ and coordinates) with the Neighbouring data

2. Overlap distribution maps with Neighbors data  
2.1. For each species we merged the Neighbors data with their known distribution (SAU distribution and catch,ESMs, and Observation)  
3. Determine transboundary if:  
3.1. Species is present in both Neighbouring EEZs by INDEX

We create two "confidence level" based on data and area covered.

@@

This part is to determine the list of species to be analyzed in the project. Initially this list was limited by the species data from the DBEM, however, as we are not using the DBEM, the limit is now the SAU.

@@

## Determine Neighbors

This is the first step of the analysis and will determine what EEZs are neighbors. The routine creates a final data-set that we then use to estimate transboundary species.

@@

This function determines what EEZs are Neighbors and returns a data.frame of it

@@

### Sub Routine; Neighbors

@@

Once those thresholds are met, the status of the species is determined as follows:

@@

The data-sets SAU_D, OCC, and ESM are used as species presence while SAU_C is used as a confirmation of that. The `Model Index` is the first threshold and estimates the uncertainty of models. Goes from 0 - 1 as follows:

- 1 or 0; All models agree that in the presence of the species
- 0.75; Three out of four models agree on species presence
- 0.50; Two out of four models agree on species presence
- 0.25; Only one model flags a species presence
- 0; All models agree there is no species there

The `Area_Index` is the second threshold and estimates the proportion of each species distribution in each EEZ. It only take into consideration the distribution of the species within the two EEZs, rather than the complete distribution. Hence, is mirror (e.g. if EEZ#1 is 0.40, EEZ#2 is 0.6)

@@

There are quite a few inconsistencies between the names of territories within the SAU shape file, the distribution data and the UN database. The following function cleans up the names, some of them manually some of the automatic. It also removes the "transboundary nature" of those species shared by two territories that belong to the same nation (e.g. Brazil mainland and Brazil (Fernando de Noronha) or US Gulf of Mexico and US East coast). Finally, there is an annoying thing coding issue between MAC and Windows related to characters so I have to also fix for that, manually.

@@

  if(Variable_Selected == "catch"){
    Map_Label <- "Catch (Thousand Tons)"
    Plot_Name <- "Catch_plot.png"
  }else{
    Map_Label <- "Revenue (Million USD)"
    Plot_Name <- "Rev_plot.png"
  }

@@

  Rev_Plot <- ggplot(
    # Regional plots
    data = Subregion_Rev_Data,
    aes(
      x=reorder(id,Value_sum),
      y=Value_sum, 
      fill=Value_sum
    )
  ) +    
    ylim(-1500, max_Rev_lim) +
    geom_bar(stat="identity") +
    # Regional averages
    geom_point(data = Subregion_Rev_Data,
               aes(
                 x=reorder(id,Value_sum),
                 y=Value_m
               ),
               colour = "black",
               alpha = 0.5
    ) +
    # Regional sds
    geom_errorbar(data = Subregion_Rev_Data,
                  aes(
                    ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd), # sets lower to 0
                    ymax=Value_m+Value_sd
                  ), 
                  width=.2,
                  position=position_dodge(.9),
                  alpha = 0.5) +
    # Looking good
    theme_minimal() +
    theme(
      legend.position = c(0.73,0.60),
      axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      plot.margin = margin(0,-10,-6,-10,"cm")
    )  +
    # Base line
    # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
    #              colour = "black", size=0.1, inherit.aes = FALSE) +
    coord_polar(start = 0) + 
    geom_text(data=label_data_rev, 
              aes(x=id,
                  y=Value_sum,
                  label=sub_region,
                  hjust=hjust), 
              color="black",
              fontface="bold",
              size=2, 
              angle= label_data_rev$angleb, 
              inherit.aes = FALSE) +
    scale_fill_gradientn("",
                         colours = pal,
                         limits = c(0,12000),
                         breaks = seq(0,12000,3000)) +
    guides(fill = guide_colorbar(label.position = "left")
    )

@@

  Catch_Plot <- ggplot(data = Subregion_Catch_Data,
                     aes(x=reorder(id,Value_sum),
                         y=Value_sum, 
                         fill=Value_sum
                     )
) +    
  ylim(-1.5, max_Catch_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Catch_Data,
             aes(
               x=reorder(id,Value_sum),
               y=Value_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sd's
  geom_errorbar(data = Subregion_Catch_Data,
    aes(
      ymin=ifelse(Value_m-Value_sd <= 0,0,Value_m-Value_sd),
      ymax=Value_m+Value_sd
    ), 
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_catch, 
            aes(x=id,
                y=ifelse(Value_sum >= 12,12,Value_sum+0.1), # Fix names overlap
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_catch$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       limits = c(0,12),
                       breaks = seq(0,12,3),
                       colours = pal
  )

@@

  plot_all <- ggdraw() +
  # map
  draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.1, y = 0.08, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.45, y = 0.08, width = 0.5, height = 0.4) +
  # Labeks
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0, 0), 
                  y = c(1, 0.45)
  ) +
  draw_plot_label(label = c("Revenue (USD) | Catch (Tons)","(Million)"), 
                  size = 8,
                  x = c(0.330,0.485), 
                  y = c(0.31,0.29)
  )

@@

In here we load and cleaned the multiple external data sets required to produce the manuscript figures

@@

## Determine Thresholds

Determine transboundary stocks and countries based on selected thresholds. We created two thresholds (levels of uncertainty), in here we can chose which level we wanna work with.

@@

# -------------------------- #
# Number of EEZs and countries
# -------------------------- #

# number of eezs
length(unique(sau_eez_fes$eez_name))
# Number of coastal territories
length(unique(sau_eez_fes$fishing_entity))

@@

###_________________###
# Discrete species
# Species that are transboundary in some cases but discrete in other cases
###_________________###

@@

# Both categories (trans and Discrete)
n_discrete <- Tresholded_T_Data %>% 
  semi_join(Discrete,
            by = "taxon_key") %>% # those that are not only discrete
  group_by(taxon_key) %>% 
  summarise(n()) %>% 
  pull(unique(taxon_key)) %>% 
  length()

###_________________###
# Discrete Exclusive
# Species that are only discrete and are not present in the transboundary category
###_________________###

@@

## double check

Discrete_Exclusive %>% 
  semi_join(Tresholded_T_Data, by = "taxon_key") # 0 ok thes

@@

Summary_Discrete_Exclusive <- Discrete_Exclusive %>% 
  left_join(SAU_Sampled_Data) %>% 
  group_by(Variable) %>%
  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
         Per_SAU = Total_Discrete/Total_Global*100)

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area, 
            by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    # Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

###

Total_Value_EEZ <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(SAU_Global_Data) %>% 
  group_by(fishing_entity,Variable) %>% 
  summarise(Total_Value = sum(Value,na.rm=T))

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area, 
            by = "fishing_entity") %>% 
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_Entity/1000000))
  ) %>% 
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
  group_by(fishing_entity,Variable,Value) %>% 
  summarise(
    Bins = cut(Value,breaks = Map_Breaks, dig.lab = 5 ),
    Bins_Plot = cut(Value,breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

@@

Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T) %>%
  # select(-Size_Entity,-Trans_Entity_n) %>% 
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),4)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

# Fix names for plot
Subregion_Trans_Value <- Subregion_Trans_raw_Value

Subregion_Trans_Value$sub_region <- Subregion_Trans_raw_Value$sub_region %>% 
  gsub("Northern","N.",.) %>% 
  gsub("Southern","S.",.) %>% 
  gsub("Western","W.",.) %>% 
  gsub("Eastern","E.",.)

@@

# Label info Rev
label_data_rev <- Subregion_Trans_Value %>% 
  filter(Variable == "value") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )#,
    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
  )

# Label info Catch
label_data_catch <- Subregion_Trans_Value %>% 
  filter(Variable == "catch") %>% 
  arrange(Value_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,number_of_bar),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    )#,
    # sub_region_n = paste(sub_region," (n=",Trans_Entity_n_sum,")",sep = "")
  )

@@

# Variable to plot (value or catch)
Variable_plot <- "value"
CreateFigureOne(Variable_plot)

@@

  p<- ggdraw() +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0, y = 0, width = 0.8, height = 1) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.4, y = 0, width =0.8, height = 1) +
  # Legend
  draw_plot(legend_plot, x = 0.2, y = 0.1, width = 0.59, height = 0.1) +
  # Labeks
  draw_plot_label(label = c("A", "B"),
                  size = 15,
                  x = c(0.1, 0.6),
                  y = c(1, 1)
  ) +
  draw_plot_label(
    label = c("Revenue (USD) | Catch (Tons)","Million per Km2"),
                  size = 6,
                  x = c(0.3,0.40),
                  y = c(0.25,0.22)
  )

@@

Top_Rev_Countries <- c("China", "Peru", "Russian Federation", "Chile", "USA","Japan")

# Total revenue from Top countries
Total_Top_Rev <- Value_Trans_Country %>% 
  filter(Variable == "value") %>% 
  filter(fishing_entity %in% Top_Rev_Countries) %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  left_join(Subregion_Trans_raw_Value) %>% 
  mutate(Per_Top = Value/Value_sum*100) %>% 
  select(1:3,Per_Top)

@@

Top5 <- c("Peru", "Russian Federation", "Japan", "USA","China")

@@

### Statistical differences within regions
We used a one-way ANOVA to determine significant differences within regions for transboundary fisheries catches and revenue with a Tukey's HSD post-hoc test.

@@

### Reveneu ANOVA

Subregion_Rev_stats <- Subregion_Data_stats %>% 
  filter(Variable == "value")

Rev_aov <- aov(Value~sub_region, data = Subregion_Rev_stats)
Rev_aov

summary(Rev_aov)
#              Df    Sum Sq Mean Sq F value   Pr(>F)    
# sub_region   16  75738982 4733686   4.948 3.46e-08 ***
# Residuals   158 151144071  956608

#  Post-hoc analysis
TukeyHSD(Rev_aov) %>% 
  tidy() %>% 
  filter(adj.p.value < 0.05)

@@

Catch_aov <- aov(Value~sub_region, data = Subregion_Catch_stats)
Catch_aov

summary(Catch_aov)
#  Df Sum Sq Mean Sq F value  Pr(>F)   
# sub_region   16  27.51  1.7195   2.265 0.00539 **
# Residuals   158 119.97  0.7593

#  Post-hoc analysis
TukeyHSD(Catch_aov) %>% 
   tidy() %>% 
  filter(adj.p.value < 0.05) # Eastern Asia

@@

#  Post-hoc analysis
TukeyHSD(Weight_aov) %>% 
  tidy() %>% 
  filter(adj.p.value < 0.05) # Northern Europe
```

@@

@@

T_Summary <- Status_Data_Plot %>% 
  mutate(value = ifelse(value <0, value*-1,value)) %>% 
  group_by(observation) %>% 
  summarise(tot=sum(value),
            mean(value),
            sd(value)) %>% 
  arrange(desc(tot))

@@

### Statistical differences between species status

Using MANOVA to investigate differences in catch category between discrete and transboundary species

@@

#-----------------# 
# Get Data
#-----------------#

# Transboundary Data
Transboundary_Data_Stats <- Status_Plot_Data %>% 
filter(observation != "No Category") %>%
  mutate(value = abs(value))

# Discrete Data
Discrete_Data_Stats <- Discrete_Status_Data %>% 
  filter(observation != "No Category") %>%
  mutate(value = abs(value))

Manova_Differences <- Transboundary_Data_Stats %>% 
  rename(Trans_value = value) %>% 
  left_join(Discrete_Data_Stats, by = c("individual","observation","group")
  ) %>% 
  rename(Discrete_value= value) %>% 
  mutate(Discrete_value = ifelse(is.na(Discrete_value),0,Discrete_value))

#-----------------# 
## Test assumptions
#-----------------#

### Correlation
